---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/evrfish/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/evrfish/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/evrfish/branch/main/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/evrfish?branch=main)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/license/mit/)
<!-- badges: end -->

# evrfish


## Introduction

`evrfish` is an R package for EVR Fish Projects.
It is intended to be used by EVR staff and contractors and anyone else
who finds it useful.

Additional information is available at <https://poissonconsulting.github.io/evrfish/>.

## Installation

To install from [GitHub](https://github.com/poissonconsulting/evrfish)

```r
# install.packages("remotes")
remotes::install_github("poissonconsulting/evrfish")
```


or from [r-universe](https://poissonconsulting.r-universe.dev/evrfish).
```r
install.packages("evrfish", repos = c("https://poissonconsulting.r-universe.dev", "https://cloud.r-project.org"))
```

## Demonstration

### Growing Season Degree Days

`gsdd()` takes data frame with a `date` and `temperature` column with
the mean daily water temperature in centigrade 
and calculates the growing season degree days (GSDD).

```{r}
library(evrfish)
gsdd(gsdd::temperature_data)
```

`gdd()` calculate the growing degree days (GDD) to a date.

```{r}
gdd(gsdd::temperature_data, end_date = as.Date("1972-08-30"))
```

`gss()` calculates the growing season(s) (GSS).

```{r}
gss(gsdd::temperature_data)
```

`gss_plots()` plots the temperature time series including growing season(s), moving average and thresholds.

```{r}
gss_plot(gsdd::temperature_data)
```

### ATUs

`date_atus()` calculates the date on which a specified number of accumulated thermal units are exceeded.

```{r}
date_atus(gsdd::temperature_data, start_date = as.Date("1972-06-15"), atus = 600)
```


## Contribution

Please report any [issues](https://github.com/poissonconsulting/evrfish/issues).

[Pull requests](https://github.com/poissonconsulting/evrfish/pulls) are always welcome.

## Code of Conduct

Please note that the evrfish project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.
